Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model

### 2021-06-25 SIR_manuscript.tex
starting on Discussion

\newcommand{\fady}[1]{\comment{cyan}{Fady}{#1}}
\newcommand{\ali}[1]{\comment{magenta}{Ali}{#1}}
\newcommand{\jd}[1]{\comment{blue}{JD}{#1}}
\newcommand{\david}[1]{\comment{orange}{DJDE}{#1}}
\newcommand{\bmb}[1]{\comment{red}{BMB}{#1}}
\newcommand{\todo}[1]{\comment{red}{TODO}{#1}}

@@

In this paper, we have defined and analyzed a simple compartmental model that combines epidemiological dynamics (as defined by a simple SIR model) with the dynamics of testing and isolation. Our model is a caricature --- it models the most basic feedbacks between epidemic and testing processes, but does not attempt to incorporate the many known complications of COVID-19 epidemiology (e.g. exposed, presymptomatic, and asymptomatic compartments \citep{kain2021chopping}; time-varying testing rates [REFS?]; behavioural dynamics \citep{weitz2020awareness}). Thus, it is most appropriate for assessing the \emph{qualitative} phenomena that arise from the interactions between epidemiology and testing, rather than for making quantitative predictions or guiding pandemic responses.

>>>>

\newcommand{\fady}[1]{\comment{cyan}{Fady}{#1}}
\newcommand{\ali}[1]{\comment{magenta}{Ali}{#1}}
\newcommand{\jd}[1]{\comment{blue}{JD}{#1}}
\newcommand{\david}[1]{\comment{orange}{DJDE}{#1}}
\newcommand{\bmb}[1]{\comment{red}{BMB}{#1}}
\newcommand{\todo}[1]{\comment{red}{TODO}{#1}}
\newcommand{\needref}{\textcolor{red}{(REFS?)}}

@@

In this paper, we have developed and analyzed a simple compartmental model that combines epidemiological dynamics---as defined by a simple SIR model---with the dynamics of testing and isolation. Our model is a caricature: it models the most basic feedbacks between epidemic and testing processes, but does not attempt to incorporate the many known complications of COVID-19 epidemiology (e.g., exposed, pre-symptomatic, and asymptomatic compartments \citep{kain2021chopping}; time-varying testing rates \needref; behavioural dynamics \citep{weitz2020awareness}). Thus, it is most appropriate for assessing the \emph{qualitative} phenomena that arise from the interactions between epidemiology and testing, rather than for making quantitative predictions or guiding pandemic responses.
